%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% XeLaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[colorlinks=true,
            linkcolor=Maroon,
            urlcolor=NavyBlue]{hyperref}
            
\usepackage{fontspec}
\setmainfont{Arial}

\name{Justin Murphy} % Your name
\address{1 University Road \\ Southampton, SO17 1BJ, UK} % Your address
\address{Building 58 \\ Office 3083} % Your secondary addess (optional)
\address{\href{http://jmrphy.net}{jmrphy.net} \\ \href{http://twitter.com/jmrphy}{@jmrphy} \\ \href{mailto:j.murphy@soton.ac.uk}{j.murphy@soton.ac.uk}} % Your phone number and emai

\begin{document}
\urlstyle{sf}


%----------------------------------------------------------------------------------------
%	LIST OF PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{List of Publications}

\raggedright

\begin{rSubsection}{Revising \& Resubmitting}{}{}{}
\item Murphy, Justin. \emph{Why are More Trade-Open Countries More Likely to Repress the Media?} \url{http://dx.doi.org/10.6084/m9.figshare.997696} (Resubmitting to \emph{International Organization})
\end{rSubsection}

\begin{rSubsection}{Currently Under Review}{}{}{}
\item Murphy, Justin. \emph{Racism and Sexism in "Stand Your Ground" Cases in Florida, 2006-2013}. \url{http://dx.doi.org/10.6084/m9.figshare.1301532}. (Under review at \emph{Social Science Quarterly})
\item Havercroft, Jonathan and Justin Murphy. \href{https://www.academia.edu/14437108/Is_the_Tea_Party_Libertarian_Authoritarian_or_Something_Else}{\emph{Is the Tea Party Libertarian, Authoritarian, or Something Else?}} (Under review at \emph{Social Science Quarterly})
\end{rSubsection}

\begin{rSubsection}{Working Papers, Completed and Submitting}{}{}{}
\item Murphy, Justin. \emph{Mass Media and the Domestic Politics of Economic Globalization.} \url{http://dx.doi.org/10.6084/m9.figshare.1181874}. 
\item Murphy, Justin. \emph{Mass Media and Civil War Onset}. \url{http://dx.doi.org/10.6084/m9.figshare.1181828}
\item Murphy, Justin and Daniel Devine. \emph{The Dynamics of Media Coverage and Party Support for the UK Independence Party}. \url{http://dx.doi.org/10.6084/m9.figshare.1375544}
\end{rSubsection}

\begin{rSubsection}{Working Papers, In-Progress}{}{}{}
\item Murphy, Justin, Jessica Ogden, and Bindi Shah. \emph{Race \& Nation on Twitter: Understanding Romanian \& Bulgarian Migration to the UK.} \url{http://jmrphy.net/migration_tweets/}
\end{rSubsection}

\begin{rSubsection}{Non-Academic Publications}{}{}{}
\item Murphy, Justin. 2015. \href{https://medium.com/blacklivesmatter/two-graphs-show-how-stand-your-ground-laws-reinforce-white-supremacy-and-patriarchy-5e60240a8405}{"Two Graphs Show How 'Stand Your Ground' Laws Reinforce White Supremacy and Patriarchy,"} in \emph{Black Lives Matter (Medium.com)}. 
\item Murphy, Justin. 2015. \href{http://www.newstatesman.com/politics/2015/04/ukip-dont-deserve-their-media-prominence-heres-proof}{"Ukip don't deserve their media prominence. Here's the proof,"} \emph{New Statesman}. 
\item Murphy, Justin. 2014. \href{http://sotonpolitics.org/2014/02/06/the-question-of-revolution-is-not-romantic-it-is-unavoidable}{"The question of revolution is not romantic, it is unavoidable,"} \emph{Politics Upside Down}. 
\item Murphy, Justin. 2013. \href{http://thesocietypages.org/cyborgology/2013/08/24/in-defense-of-a-strategic-digital-dualism/}{"In Defense of a Strategic Digital Dualism,"} \emph{Cyborgology}. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
